---
title: "Simple-Run"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simple-Run}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r load_packages, message = FALSE, warning = FALSE}

library(tidyverse)
library(usethis)
library(devtools)
devtools::install_github("TranscriptionFactory/LassoReg", force = F,
                         dependencies = F, quiet = T)

library(LassoReg, attach.required = T)
library(Matrix)

```

## Load data
First note: alpha here refers to a multiplier on the lambda chosen through cross validation.

Second note: some values of alpha may be too stringent for your data and result in no 
features being selected and a resulting error in calculating the svm. If this happens,
try using a smaller value. 
You can test multiple values for alpha during a run.
Here's some ideas for values to try (I usually increase/decrease in increments of 0.25)
1. 0.75, 1.0, 1.25
2. 0.5, 0.75, 1.0

If you're getting good classification, use larger values

In general, 
# Larger alpha/lambda values = fewer features selected
and vice versa
```{r load_data, include = TRUE}
df = as.data.frame(LassoReg::example_data)

alphaValues = c(0.75)

# usually use
#alphaValues = c(0.75, 1.0, 1.25)
```

## Run Lasso

```{r run_lasso, message = FALSE, warning = FALSE}

results = LassoReg::LASSO_Grid(df, alphaValues = alphaValues)

```

## Analyze features

```{r analyze_features, include = TRUE, echo = TRUE}
chosen_vars = LassoReg::extractVars(results)

head(chosen_vars)
```

## Analyse Results

```{r analyze_results, include = TRUE}

plots = LassoReg::plotResults(results, df)

# multiple plots get returned
```

```{r, fig.width = 8, fig.height = 4}
plots[[1]]
```

```{r, fig.width = 8, fig.height = 5}
plots[[2]]
```

```{r, fig.width = 8, fig.height = 5}
plots[[3]]
```
